\newpage 
\large{\textbf{Publication list}}

\large{\textbf{Journals}}
\normalsize
\begin{enumerate}
\item \underline{Kentaro Yoshioka}, Tomohiko Sugimoto, Naoya Waki, Sinnyoung Kim, Daisuke Kurose, Hirotomo Ishii, Masanori Furuta, Akihide Sai, Hiroki Ishikuro, Tetsuro Itakura, “Digital Amplifier: An Power-Efficient and Process-Scaling Amplifier for Switched Capacitor Circuits,” in \textit{IEEE Trans. VLSI Systems}, Accepted. (Chapter 2)
\item \underline{Kentaro Yoshioka}, Ryo Saito, Takumi Danjo, Sanroku Tsukamoto, Hiroki Ishikuro, “Dynamic architecture and frequency scaling in 0.8–1.2 GS/s 7 b subranging ADC,” in \textit{IEEE Journal of Solid-State Circuits}, vol. 50, no. 4, pp. 932‒945, Apr. 2015. (Chapter 3)
\item \underline{Kentaro Yoshioka}, Akira Shikata, Ryota Sekimoto, Tadahiro Kuroda, Hiroki Ishikuro, “An 8 bit 0.3–0.8 V 0.2–40 MS/s 2-bit/step SAR ADC with successively activated threshold configuring comparators in 40 nm CMOS,” in \textit{IEEE Trans. VLSI Systems}, vol. 23, no. 2, pp. 356-368, Feb. 2015. (Chapter 4)
\end{enumerate}

\large{\textbf{International Conferences}}
\normalsize

\begin{enumerate}
\item	\underline{Kentaro Yoshioka}, Tomohiko Sugimoto, Naoya Waki, Sinnyoung Kim, Daisuke Kurose, Hirotomo Ishii, Masanori Furuta, Akihide Sai, Tetsuro Itakura, “A 0.7 V 12b 160MS/s 12.8 fJ/conv-step pipelined-SAR ADC in 28nm CMOS with digital amplifier technique,” in \textit{IEEE International  Solid-State  Circuits  Conference  Digest  of  Technical Papers (ISSCC)}, 2017.

\item \underline{Kentaro Yoshioka},  Ryo  Saito,  Takumi  Danjo,  Sanroku  Tsukamoto,  and  Hi-roki Ishikuro,  “7-bit 0.8–1.2 GS/s dynamic architecture and frequency scaling subrange  ADC  with  binary-search/flash  live  configuring  technique,” in \textit{IEEE Symposium on VLSI Circuits (VLSIC)}, 2014.

\item	\underline{Kentaro Yoshioka}, Akira Shikata, Ryota Sekimoto, Tadahiro Kuroda, Hiroki Ishikuro, “An 8b Extremely Area Efficient Threshold Configuring SAR ADC with Source Voltage Shifting Technique,” in \textit{IEEE ASP-DAC}, 2014.

\item	\underline{Kentaro Yoshioka}, Akira Shikata, Ryota Sekimoto, Tadahiro Kuroda, Hiroki Ishikuro, “A 0.0058mm2 7.0 ENOB 24MS/s 17fJ/conv. Threshold Configuring SAR ADC with Source Voltage Shifting and Interpolation Technique,” in \textit{IEEE Symposium on VLSI Circuits (VLSIC)}, 2013.

\item	\underline{Kentaro Yoshioka}, Akira Shikata, Ryota Sekimoto, Tadahiro Kuroda, Hiroki Ishikuro, “A 0.35-0.8 V 8b 0.5-35MS/s 2bit/step extremely-low power SAR ADC,” in \textit{IEEE ASP-DAC}, 2013.

\item \underline{Kentaro Yoshioka}, Akira Shikata, Ryota Sekimoto, Tadahiro Kuroda, Hiroki Ishikuro, “An 8bit 0.35–0.8 V 0.5–30MS/s 2bit/step SAR ADC with wide range threshold configuring comparator,” in \textit{Proceedings of ESSCIRC}, 2012.

\end{enumerate}
\\
\\
\large{\textbf{Awards}}
\normalsize

1. Special Feature Award, \textit{IEEE ASP-DAC}.

2. Co-recipient: Best Student Award, \textit{IEEE A-SSCC 2012}.
\vspace*{\fill} \newpage \rm

\large{\textbf{Other works}}

\large{\textbf{Journals}}
\normalsize

\begin{enumerate}
\item	Yosuke Toyama, \underline{Kentaro Yoshioka}, Koichiro Ban, Akihide Sai, Kohei Onizuka “An 8-Bit 12.4 TOPS/W Phase-Domain MAC Circuit for Energy-Constrained Deep Learning Accelerators,” \textit{IEEE Journal of Solid-State Circuits}, Accepted.

\item	\underline{Kentaro Yoshioka}, Hiroshi Kubota, Tomonori Fukushima, Satoshi Kondo, Tuan Thanh Ta, et al, “A 20-ch TDC/ADC Hybrid Architecture LiDAR SoC for 240x96 Pixel 200-m Range Imaging With Smart Accumulation Technique and Residue Quantizing SAR ADC,” \textit{IEEE Journal of Solid-State Circuits}, vol. 53, no. 11, pp. 3026‒3038, Nov. 2018.

\item	Shusuke Kawai, Rui Ito, Kengo Nakata, Yutaka Shimizu, Motoki Nagata, Tomohiko Takeuchi, Hiroyuki Kobayashi, Katsuyuki Ikeuchi, Takayuki Kato, Yosuke Hagiwara, Yuki Fujimura, \underline{Kentaro Yoshioka}, Shigehito Saigusa, Hiroshi Yoshida, Makoto Arai, Toshiyuki Yamagishi, Hirotsugu Kajihara, Kazuhisa Horiuchi, Hideki Yamada, Tomoya Suzuki, Yuki Ando, Kensuke Nakanishi, Koichiro Ban, Masahiro Sekiya, Yoshimasa Egashira, Tsuguhide Aoki, Kohei Onizuka, Toshiya Mitomo, “An 802.11ax 44 High-Efficiency WLAN AP Transceiver SoC Supporting 1024-QAM With Frequency-Dependent IQ Calibration and Integrated Interference Analyzer,” \textit{IEEE Journal of Solid-State Circuits}, vol. 53, no. 12, pp. 3688-3699, Dec. 2018.

\item	Ryota Sekimoto, Akira Shikata, \underline{Kentaro Yoshioka}, Tadahiro Kuroda, Hiroki Ishikuro, “A 0.5-V 5.2-fJ/conversion-step full asynchronous SAR ADC with leakage power reduction down to 650 pW by boosted self-power gating in 40-nm CMOS,” \textit{IEEE Journal of Solid-State Circuits}, vol. 48, no. 11, pp. 2628-2636, Nov. 2013.

\item	Ryota Sekimoto, Akira Shikata, \underline{Kentaro Yoshioka}, Tadahiro Kuroda, Hiroki Ishikuro, “An adaptive DAC settling waiting time optimized ultra low voltage asynchronous SAR ADC in 40 nm CMOS,” \textit{IEICE Trans. Electronics}, Vol.96, pp.820-827, June 2013.

\item	Akira Shikata, Ryota Sekimoto, \underline{Kentaro Yoshioka}, Tadahiro Kuroda, Hiroki Ishikuro, “A 4–10 bit, 0.4–1 V Power Supply, Power Scalable Asynchronous SAR-ADC in 40 nm-CMOS with Wide Supply Voltage Range SAR Controller,” \textit{IEICE Trans. Electronics}, Vol.96, pp.443-452, Feb 2013.
\end{enumerate}
\\
\\
\large{\textbf{International Conferences}}
\normalsize

\begin{enumerate}
\item	\underline{Kentaro Yoshioka}, Edward Lee, Simon Wong, Mark Horowitz, “Dataset Culling: Towards Efficient Training Of Distillation-Based Domain Specific Models,” \textit{To be presented at IEEE International Conference on Image Processing (ICIP)}, 2019.

\item Yosuke Toyama, \underline{Kentaro Yoshioka}, Koichiro Ban, Akihide Sai, Kohei Onizuka, “A 12.4 TOPS/W, 20\% Less Gate Count Bidirectional Phase Domain MAC Circuit for DNN Inference Applications,” in \textit{IEEE Asian  Solid-State  Circuits Conference (A-SSCC)}, 2018.

\item	\underline{Kentaro Yoshioka}, Yosuke Toyama, Koichiro Ban, Daisuke Yashima, Shigeru Maya, Akihide Sai, Kohei Onizuka, “PhaseMAC: A 14 TOPS/W 8bit GRO based Phase Domain MAC Circuit for In-Sensor-Computed Deep Learning Accelerators,” in \textit{IEEE Symposium on VLSI Circuits (VLSIC)}, 2018.

\item	\underline{Kentaro Yoshioka}, Hiroshi Kubota, Tomonori Fukushima, Satoshi Kondo, Tuan Thanh Ta, Hidenori Okuni, Kaori Watanabe, Yoshinari Ojima, Katsuyuki Kimura, Sohichiroh Hosoda, Yutaka Oota, Tomohiro Koizumi, Naoyuki Kawabe, Yasuhiro Ishii, Yoichiro Iwagami, Seitaro Yagi, Isao Fujisawa, Nobuo Kano, Tomohiro Sugimoto, Daisuke Kurose, Naoya Waki, Yumi Higashi, Tetsuya Nakamura, Yoshikazu Nagashima, Hirotomo Ishii, Akihide Sai, Nobu Matsumoto, “A 20ch TDC/ADC hybrid SoC for 240x96-pixel 10\%-reflection $<$ 0.125\%-precision 200m-range imaging LiDAR with smart accumulation technique,” in \textit{IEEE International  Solid-State  Circuits  Conference  Digest  of  Technical Papers (ISSCC)}, 2018.

\item	Shusuke Kawai, Hiromitsu Aoyama, Rui Ito, Yutaka Shimizu, Mitsuyuki Ashida, Asuka Maki, Tomohiko Takeuchi, Hiroyuki Kobayashi, Go Urakawa, Hiroaki Hoshino, \underline{Kentaro Yoshioka}, et al, “An 802.11 ax 4×4 spectrum-efficient WLAN AP transceiver SoC supporting 1024 QAM with frequency-dependent IQ calibration and integrated interference analyzer,” in \textit{IEEE International  Solid-State  Circuits  Conference  Digest  of  Technical Papers (ISSCC)}, 2018.

\item	\underline{Kentaro Yoshioka}, Hiroki Ishikuro, “A 13b SAR ADC with eye-opening VCO based comparator,” in \textit{Proceedings of ESSCIRC}, 2014.

\item	M Nomura, A Muramatsu, H Takeno, S Hattori, D Ogawa, M Nasu, K Hirairi, S Kumashiro, S Moriwaki, Y Yamamoto, S Miyano, Y Hiraku, I Hayashi, \underline{K. Yoshioka}, A Shikata, Hiroki Ishikuro, M Ahn, Y Okuma, X Zhang, Y Ryu, K Ishida, M Takamiya, Tadahiro Kuroda, H Shinohara, T Sakurai, “0.5 V image processor with 563 GOPS/W SIMD and 32bit CPU using high voltage clock distribution (HVCD) and adaptive frequency scaling (AFS) with 40nm CMOS,” in \textit{IEEE Symposium on VLSI Circuits (VLSIC)}, 2013.

\item \underline{Kentaro Yoshioka}, Yosuke Toyama, Teruo Jyo, Hiroki Ishikuro, “A voltage scaling 0.25–1.8 V delta-sigma modulator with inverter-opamp self-configuring amplifier,” in \textit{IEEE ISCAS}, 2013.

\item	Ryota Sekimoto, Akira Shikata, \underline{Kentaro Yoshioka}, Tadahiro Kuroda, Hiroki Ishikuro, “A 40nm CMOS full asynchronous nano-watt SAR ADC with 98\% leakage power reduction by boosted self power gating,” in \textit{IEEE Asian  Solid-State  Circuits Conference (A-SSCC)}, 2012.
\end{enumerate}



\vspace*{\fill} \newpage \rm